Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2019-02-07 main.tex
Updates from Overleaf

North America is characterized by a large, high-wavespeed lithospheric craton,
bounded by the Rocky Mountain Front to the West and continental
margin to the East. On both sides the lithosphere has been deformed by
low wavespeed structures, thus forming sharp tectonic boundaries
~\citep{grand1984upper, masters1996shear, grand1997high,
megnin2000three, gu2001models, schaeffer2014imaging, zhu2017radial}.

>>>>

North America is characterized by a large, high-wavespeed lithospheric craton,
bounded by the Rocky Mountain Front to the West and continental
margin to the East. On both sides the lithosphere has been deformed by
low wavespeed structures, thus forming sharp tectonic boundaries
~\citep{grand1984upper,masters1996shear,grand1997high,
megnin2000three,gu2001models,schaeffer2014imaging,zhu2017radial}.
